### 2016-06-21 Paper_v1.tex
Jun. 21st afternoon

@@

\end{document}

>>>>

\begin{figure}[ht]
\centering
\includegraphics[width=1.00\textwidth]{./Figures/AAs_bounded.pdf}
\caption{Total-order global sensitivities of protein export flux to amino acid import fluxes, with flux upper bounds set to 0.5 mM/hr.}
\label{fig:AAs_bounded}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics[width=1.00\textwidth]{./Figures/AAs_unbounded.pdf}
\caption{Total-order global sensitivities of protein export flux to amino acid import fluxes, with each amino acid flux unbounded respectively.}
\label{fig:AAs_unbounded}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics[width=1.00\textwidth]{./Figures/C_Secretion.pdf}
\caption{Total-order global sensitivities of protein export flux to glutamic acid, oxygen and glucose import fluxes, and translation initiation rate, in the case of four organic acid export flux upper bounds set to 0.1 mM/hr, whereas organic acid export fluxes are unbounded in the control.}
\label{fig:C_Secretion.pdf.pdf}
\end{figure}

@@

\end{document}
\grid
\grid
